Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-08-01 msbr_reproc.tex
Spectrum graph corrected (normalize to 1 using trapz)

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The thermal spectrum \gls{MSR} is an advanced type of reactor that consists of 
constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or 
$LiF-BeF_2-ZrF_4-UF_4$) and solid graphite moderator structures. This liquid 
fuel form leads to immediate advantages over traditional, 
solid-fueled, reactors. The molten-salt carrier with dissolved 
fissile and/or fertile material allows for online refuelling and 
reprocessing. Thus, \glspl{MSR} can potentially operate years without shutdown, 
achieving maximum fuel utilization and outstanding neutron economy 
\cite{leblanc_molten_2010}. Moreover, this type of fuel does not need 
complex fabrication since the fissile material could be transported from any 
enrichment plant to the \gls{NPP} in the form 
of uranium hexafluoride ($UF_6$).  Additionally, \glspl{MSR} have a high level 
of inherent safety due to their characteristically 
strong negative temperature coefficient of reactivity, near-atmospheric 
pressure in the primary loop, stable coolant, passive decay heat cooling, and 
small excess reactivity \cite{elsheikh_safety_2013}.

The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} 
specifically to realize the promise of the thorium fuel cycle which allows the 
use of natural thorium instead of enriched uranium as the fertile element. 
Thorium breeds the fissile $^{233}U$ and avoids uranium enrichment 
\cite{robertson_conceptual_1971}. In the matter of nuclear fuel cycle, the 
thorium cycle produces a reduced quantity of plutonium and \glspl{MA} 
compared to the traditional uranium fuel cycle. Consequently, it may 
significantly increase proliferation resistance when the \gls{MSR} operates in the 
breeder regime. The \glspl{MSR} also could be employed as a converter reactor for 
transmutation or spent fuel from current \glspl{LWR}.

Recently, interest in \glspl{MSR} has resurged, with multiple new companies 
pursuing commercialization of \gls{MSR} designs\footnote{Examples include both 
liquid-fueled molten salt designs from Transatomic, Terrapower, Terrestrial, 
and Thorcon.}.
To further develop these \gls{MSR} concepts, particularly with respect to their  
strategies for online reprocessing and refueling, computational analysis methods capturing
their unique reactor physics and process chemistry are needed.
However, most contemporary nuclear reactor physics software is unable to 
perform depletion calculations in an online reprocessing 
regime. Powers \emph{et al.} suggested a novel method for conducting 
depletion simulations for \gls{MSR}. This suggested method takes into account 
fuel salt composition changes due to online 
reprocessing and refueling based on the deterministic computer code NEWT in 
SCALE \cite{powers_new_2013}. This approach was later used by Jeong \emph{et 
al.} to find an equilibrium fuel composition for the \gls{MSBR} and was 
validated with an \gls{MCNP}/CINDER90 model \cite{jeong_equilibrium_2016}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Description of the actual work}
The \gls{MSBR} is a thermal spectrum reactor. The reactor vessel has a diameter of 
$680 cm$ and a height of $610 cm$. It contains a molten fluoride fuel-salt mixture 
which performs two functions: to generate heat in the moderated region and to 
transport heat energy from the core to primary heat exchanger using the primary 
salt pump. The vessel also contains graphite blocks for neutron moderation and 
reflection. The lithium in the fuel-salt solution is enriched to 99.995\% 
$^7$Li because $^6$Li is a very strong neutron poison and becomes tritium upon 
neutron bombardment. In this study, the 0.005\% atomic fraction of $^6$Li has 
been taken into account because even such a small amount of isotope with very 
high absorption cross section can significantly impact the neutron flux energy 
distribution and, consequently, depletion calculation results. 
Table~\ref{tab:data} is the summary of the major \gls{MSBR} parameters used by 
this model \cite{robertson_conceptual_1971}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\captionsetup[table]{
        labelsep = newline,
        name = TABLE, justification=justified,
        singlelinecheck=false,%%%%%%% a single line is centered by default
        labelsep=colon,%%%%%%
skip = \medskipamount}
\begin{table}[h!]
        %\centering
        %\begin{tabular}{p{0.46\linewidth} p{0.50\linewidth}} \toprule
        \begin{tabularx}{\linewidth}{l X} \toprule 
                Thermal capacity of reactor           & 2250 MW(t)
                \\ \midrule
                %Net electrical output                 & 1000 MW(e) \\ \midrule
                %Net thermal efficiency        & 44.4\%
                %\\ \midrule
                Salt volume fraction in central core zone     & 0.132
                \\ \midrule
                Salt volume fraction in outer core zone       & 0.37
                \\ \midrule
                Fuel-salt inventory (Zone I)                  & 8.2 m$^3$	
                \\ \midrule
                Fuel-salt inventory (Zone II)                 & 10.8 m$^3$	
                \\ \midrule
                Fuel salt components                  & 
                LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$-$^{239}$PuF$_3$	\\ 
                \midrule
                Fuel salt composition                 & 
                71.767-16-12-0.232-0.0006 mole\%
                \\
                \bottomrule
        \end{tabularx}
        \caption{Summary of principal data for MSBR.}
        \label{tab:data}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \gls{MSBR} core consists of two different zones. The central 
zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 
Zone I composed of 1320 graphite cells, 2 graphite control rods, and 
2 safety rods consisting of boron carbide clad. The under-moderated zone, Zone 
II, with 37\% fuel salt, and radial reflector, surrounds the Zone I core region 
and serves to diminish neutron leakage. In this work, 
only a Zone I element with a $3.42138 cm$ diameter central fuel channel and molten-salt 
fuel volume fraction of 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
geometry of the unit cell model. The boundary condition of the unit cell is 
periodic. The density of the fuel salt is $3.3304 g/cm^3$ and the graphite density is 
$1.843 g/cm^3$. The temperature of fuel and graphite is fixed at 908K for the whole 
reprocessing cycle \cite{robertson_conceptual_1971}.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=0.90\linewidth]{zone_I_mesh.png}
        \caption{MSBR unit cell of Zone I geometry.}
        \label{fig:zoneI}
\end{figure}

@@

Currently, researchers 
investigating the \glspl{MSR} 
typically develop custom supporting tools and scripts to simulate 
online reprocessing and refueling. Most utilize stochastic (i.e. 
\gls{MCNP}) or deterministic (i.e. SCALE) methods for depletion and supplement 
these with custom Python scripts to capture the impacts of reprocessing 
\cite{jeong_equilibrium_2016,park_whole_2015}. Serpent 2 is the 
first commonly used monte carlo software to support continuous material 
reprocessing. It does so by allowing the user to 
define multiple material flows into and out of the fuel. This work applies this 
Serpent 2 feature to the \gls{MSBR}.

The \gls{MSBR} has the capability to remove all poisons
(e.g. 
$^{135}$Xe), noble metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) 
every 20 seconds. The $^{232}$Th in the fuel absorbs thermal 
neutrons and produces $^{233}$Pa which then decay into the fissile $^{233}$U. 
Protactinium presents a challenge, since it has a large absorption cross section in the thermal 
energy spectrum. Accordingly, $^{233}$Pa is continuously removed from the fuel salt 
into a protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without 
poisoning the reactor. The reactor reprocessing system is designed to separate 
$^{233}$Pa from the molten-salt fuel over 3 days, hold it while $^{233}$Pa 
decays into $^{233}$U, and return it back to the primary loop. This feature allows the reactor to 
avoid neutron losses to protactinium, keeps fission products to a very low level, and 
increases the efficiency of $^{233}$U breeding \cite{robertson_conceptual_1971}.

@@

This analysis models a single representative unit cell rather than the whole 
\gls{MSBR} core. Consequently, it does not take into consideration different 
fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
initial multiplication factor during depletion calculation is selected for 
a state with fully withdrawn control rods, which gives 
considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
Standard deviation for these calculations is approximately 100 pcm.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{keff.png}
        \caption{Infinite multiplication factor during a 4-years depletion 
        simulation.}
        \label{fig:keff}
\end{figure}

@@

Figure~\ref{fig:keff} shows the infinite multiplication factor for 4-year 
reprocessing cycle calculated by Serpent 2 with ENDF/B-VII.0 nuclear data. A 
significant standard deviation (100 pcm) causes the multiplication factor 
fluctuations visible in this plot.  Protactinium-233 continuously removing into 
the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
beta decays into $^{233}$U which as fresh fuel goes back to the reactor core. 
The infinite multiplication factor decreases first 400 days of depletion due to 
strong absorbers (e.g. $^{233}$Th, $^{234}$U) accumulation which causes 
relatively high fuel ($^{233}$U) refill inflow to keep reactor critical. During 
reactor operation producing fissile materials other than $^{233}$U in the core 
(e.g. $^{235}$U, $^{239}$Pu) which makes it possible to decrease fresh fuel 
refill rate after ~1 year of operation.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{fuel_composition.png}
        \caption{Normalized number density of major isotopes during 4 years of 
        depletion.}
        \label{fig:compos}
\end{figure}

@@

The analysis of the fuel salt composition variation gives clearer information 
about the equilibrium core state. Figure~\ref{fig:compos} shows the normalized 
number density of isotopes influential to core 
neutronics at the beginning of each depletion time interval. The number density 
of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount 
of it is produced during the 3-day reprocessing period. In this assessment, the multiplication 
factor stabilizes after approximately 950 days. 
Figure~\ref{fig:rates} represents the rates of online reprocessing material flows
flows over the 4-year depletion calculation. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\captionsetup[table]{
%  labelsep = newline,
%  name = TABLE, justification=justified,
%  singlelinecheck=false,%%%%%%% a single line is centered by default
%  labelsep=colon,%%%%%%
%  skip = \medskipamount}
%\begin{table}[h!]
%\centering
%\begin{tabular}{p{0.25\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
%      Isotope & First 400 days     & After 400 days          
%\\ \midrule
%$^{232}$Th  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$Pa  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$U  & $1.05134\pm0.00116$ & $1.00736$
%\\
%\bottomrule
%\end{tabular}
%  \caption{Materials flows rates during \gls{MSBR} online reprocessing 
%  [1/s*cm$^3$].}
%  \label{tab:rates}
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{rates_fuel.png}
        \caption{Materials flows rates during online reprocessing.}
        \label{fig:rates}
\end{figure}
In Figure~\ref{fig:rates} we can see that, to keep the reactor critical, a higher $^{233}$U 
flow rate from the protactinium decay tank was required for first 400 days of 
operation. After that, the $^{233}$U flow rate can be reduced. The $^{232}$Th 
rate slightly decreases over 4 years of operation due to other than $^{233}$U 
fissile materials accumulation.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{rates_outflow.png}
        \caption{Materials flows rates for the protactinium decay tank during 
        \gls{MSBR} online reprocessing.}
        \label{fig:outflow}
\end{figure}
As shown in Figure~\ref{fig:outflow}, the tank for protactinium decay 
accumulates $^{233}$Pa for approximately 200 days. Fresh $^{233}$U fuel flow is 
also established after 200 days. Uranium produced in the tank by protactinium 
decay is separated by circulation of the salt through a flourinator. The fully 
processed molten salt, on its way back to the primary loop, has uranium added 
at the rate required to maintain or adjust the fissile material concentration 
and, hence, the reactivity, in the reactor core as desired.

>>>>

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The thermal spectrum \gls{MSR} is an advanced type of reactor that consists of 
constantly circulating liquid fuel (i.e., mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ or 
LiF-BeF$_2$-ZrF$_4$-UF$_4$) and solid graphite moderator structures. This liquid 
fuel form leads to immediate advantages over traditional, 
solid-fueled, reactors. The molten-salt carrier with dissolved 
fissile and/or fertile material allows for online refueling and 
reprocessing. Thus, \glspl{MSR} can potentially operate years without shutdown, 
achieving maximum fuel utilization and outstanding neutron economy 
\cite{leblanc_molten_2010}. Moreover, this type of fuel does not need 
complex fabrication since the fissile material could be transported from any 
enrichment plant to the \gls{NPP} in the form 
of uranium hexafluoride (UF$_6$).  Additionally, \glspl{MSR} have a high level 
of inherent safety due to their characteristically 
the strong negative temperature coefficient of reactivity, near-atmospheric 
pressure in the primary loop, stable coolant, passive decay heat cooling, and 
small excess reactivity \cite{elsheikh_safety_2013}.

The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} 
specifically to realize the promise of the thorium fuel cycle which allows the 
use of natural thorium instead of enriched uranium as the fertile element. 
Thorium breeds the fissile $^{233}$U and avoids uranium enrichment 
\cite{robertson_conceptual_1971}. In the matter of nuclear fuel cycle, the 
thorium cycle produces a reduced quantity of plutonium and \glspl{MA} 
compared to the traditional uranium fuel cycle. Consequently, it may 
significantly increase proliferation resistance when the \gls{MSR} operates in the 
breeder regime. The \glspl{MSR} also could be employed as a converter reactor for 
transmutation or spent fuel from current \glspl{LWR}.

Recently, interest in \glspl{MSR} has resurged, with multiple new companies 
pursuing commercialization of \gls{MSR} designs\footnote{Examples include both 
liquid-fueled molten salt designs from Transatomic, Terrapower, Terrestrial, 
and Thorcon.}.
To further develop these \gls{MSR} concepts, particularly with respect to their  
strategies for online reprocessing and refueling, computational analysis methods capturing
their unique reactor physics and process chemistry are needed.
However, most contemporary nuclear reactor physics software is unable to 
perform depletion calculations in an online reprocessing 
regime. Powers \emph{et al.} suggested a novel method for conducting 
depletion simulations for \gls{MSR}. This suggested method takes into account 
fuel salt composition changes due to online 
reprocessing and refueling based on the deterministic computer code NEWT in 
SCALE \cite{powers_new_2013}. This approach was later used by Jeong \emph{et 
al.} to find an equilibrium fuel composition for the \gls{MSBR} and was 
validated with a \gls{MCNP}/CINDER90 model \cite{jeong_equilibrium_2016}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Description of the actual work}
The \gls{MSBR} is a thermal spectrum reactor. The reactor vessel has a diameter of 
680 cm and a height of 610 cm. It contains a molten fluoride fuel-salt mixture 
which performs two functions: to generate heat in the moderated region and to 
transport heat energy from the core to primary heat exchanger using the primary 
salt pump. The vessel also contains graphite blocks for neutron moderation and 
reflection. The lithium in the fuel-salt solution is enriched to 99.995\% 
$^7$Li because $^6$Li is a very strong neutron poison and becomes tritium upon 
neutron bombardment. In this study, the 0.005\% atomic fraction of $^6$Li has 
been taken into account because even such a small amount of isotope with very 
high absorption cross section can significantly impact the neutron flux energy 
distribution and, consequently, depletion calculation results. 
Table~\ref{tab:data} is the summary of the major \gls{MSBR} parameters used by 
this model \cite{robertson_conceptual_1971}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\captionsetup[table]{
        labelsep = newline,
        name = TABLE, justification=justified,
        singlelinecheck=false,%%%%%%% a single line is centered by default
        labelsep=colon,%%%%%%
skip = \medskipamount}
\begin{table}[h!]
        %\centering
        %\begin{tabular}{p{0.46\linewidth} p{0.50\linewidth}} \toprule
        \caption{Summary of principal data for MSBR.}
        \begin{tabularx}{\linewidth}{l X} \toprule 
                Thermal capacity of reactor           & 2250 MW(t)
                \\ \midrule
                %Net electrical output                 & 1000 MW(e) \\ \midrule
                %Net thermal efficiency        & 44.4\%
                %\\ \midrule
                Salt volume fraction in central core zone     & 0.132
                \\ \midrule
                Salt volume fraction in outer core zone       & 0.37
                \\ \midrule
                Fuel-salt inventory (Zone I)                  & 8.2 m$^3$	
                \\ \midrule
                Fuel-salt inventory (Zone II)                 & 10.8 m$^3$	
                \\ \midrule
                Fuel salt components                  & 
                LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$-$^{239}$PuF$_3$	\\ 
                \midrule
                Fuel salt composition                 & 
                71.767-16-12-0.232-0.0006 mole\%
                \\
                \bottomrule
        \end{tabularx}
        \label{tab:data}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \gls{MSBR} core consists of two different zones. The central 
zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 
Zone I composed of 1320 graphite cells, 2 graphite control rods, and 
2 safety rods consisting of boron carbide clad. The under-moderated zone, Zone 
II, with 37\% fuel salt, and radial reflector, surrounds the Zone I core region 
and serves to diminish neutron leakage. In this work, 
only a Zone I element with a 3.42138 cm diameter central fuel channel and molten-salt 
fuel volume fraction of 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
geometry of the unit cell model. The boundary condition of the unit cell is 
periodic. The density of the fuel salt is 3.3304 g/cm$^3$ and the graphite density is 
1.843 g/cm$^3$. The temperature of fuel and graphite is fixed at 908K for the whole 
reprocessing cycle \cite{robertson_conceptual_1971}.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=0.95\linewidth]{zone_I_mesh.png}
        \caption{MSBR unit cell of Zone I geometry.}
        \label{fig:zoneI}
\end{figure}

@@

Currently, researchers 
investigating the \glspl{MSR} 
typically develop custom supporting tools and scripts to simulate 
online reprocessing and refueling. Most utilize stochastic (i.e. 
\gls{MCNP}) or deterministic (i.e. SCALE) methods for depletion and supplement 
these with custom Python scripts to capture the impacts of reprocessing 
\cite{jeong_equilibrium_2016,park_whole_2015}. Serpent 2 is the 
first commonly used Monte Carlo software to support continuous material 
reprocessing. It does so by allowing the user to 
define multiple material flows into and out of the fuel. This work applies this 
Serpent 2 feature to the \gls{MSBR}.

The \gls{MSBR} has the capability to remove all poisons
(e.g. 
$^{135}$Xe), noble metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) 
every 20 seconds. The $^{232}$Th in the fuel absorbs thermal 
neutrons and produces $^{233}$Pa which then decays into the fissile $^{233}$U. 
Protactinium presents a challenge, since it has a large absorption cross section in the thermal 
energy spectrum. Accordingly, $^{233}$Pa is continuously removed from the fuel salt 
into a protactinium decay tank and allowing $^{233}$Pa to decay to $^{233}$U without 
poisoning the reactor. The reactor reprocessing system is designed to separate 
$^{233}$Pa from the molten-salt fuel over 3 days, hold it while $^{233}$Pa 
decays into $^{233}$U, and return it back to the primary loop. This feature allows the reactor to 
avoid neutron losses to protactinium, keeps fission products to a very low level, and 
increases the efficiency of $^{233}$U breeding \cite{robertson_conceptual_1971}.

@@

This analysis models a single representative unit cell rather than the whole 
\gls{MSBR} core. Consequently, it does not take into consideration different 
fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
initial multiplication factor during depletion calculation is selected for 
a state with fully withdrawn control rods, which gives 
considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
Standard deviation for these calculations is approximately 100 pcm.Figure~\ref{fig:keff} 
shows the infinite multiplication factor for 1200-days reprocessing cycle calculated by 
Serpent 2 with ENDF/B-VII.0 nuclear data. A 
significant standard deviation (100 pcm) causes the multiplication factor 
fluctuations visible in this plot.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{keff.png}
        \caption{Infinite multiplication factor during a 1200 days depletion
        simulation.}
        \label{fig:keff}
\end{figure}

@@

Protactinium-233 continuously removing into the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
beta decays into $^{233}$U which as fresh fuel goes back to the reactor core. 
The infinite multiplication factor decreases first 400 days of depletion due to 
strong absorbers (e.g. $^{233}$Th, $^{234}$U) accumulation which causes 
relatively high fuel ($^{233}$U) refill inflow to keep reactor critical. During 
reactor operation producing fissile materials other than $^{233}$U in the core 
(e.g. $^{235}$U, $^{239}$Pu) which makes it possible to decrease fresh fuel 
refill rate after ~1 year of operation.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{fuel_composition.png}
        \caption{Normalized number density of major isotopes during 1200 days of 
        depletion.}
        \label{fig:compos}
\end{figure}

@@

The analysis of the fuel salt composition variation gives clearer information 
about the equilibrium core state. Figure~\ref{fig:compos} shows the normalized 
number density of isotopes influential to core 
neutronics at the beginning of each depletion time interval. The number density 
of protactinium is very low (less than 10$^{16}$ 1/cm$^3$) but some small amount 
of it is produced during the 3-day reprocessing period. In this assessment, the multiplication 
factor stabilizes after approximately 950 days. 
Figure~\ref{fig:rates} represents the rates of online reprocessing material flows
flows over the 4-year depletion calculation. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\captionsetup[table]{
%  labelsep = newline,
%  name = TABLE, justification=justified,
%  singlelinecheck=false,%%%%%%% a single line is centered by default
%  labelsep=colon,%%%%%%
%  skip = \medskipamount}
%\begin{table}[h!]
%\centering
%\begin{tabular}{p{0.25\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
%      Isotope & First 400 days     & After 400 days          
%\\ \midrule
%$^{232}$Th  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$Pa  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$U  & $1.05134\pm0.00116$ & $1.00736$
%\\
%\bottomrule
%\end{tabular}
%  \caption{Materials flows rates during \gls{MSBR} online reprocessing 
%  [1/s*cm$^3$].}
%  \label{tab:rates}
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.04\linewidth]{rates_fuel.png}
        \caption{Materials flows rates during online reprocessing.}
        \label{fig:rates}
\end{figure}
In Figure~\ref{fig:rates} we can see that, to keep the reactor critical, a higher $^{233}$U 
flow rate from the protactinium decay tank was required for first 400 days of 
operation. After that, the $^{233}$U flow rate can be reduced. The $^{232}$Th 
rate slightly decreases over 4 years of operation due to other than $^{233}$U 
fissile materials accumulation.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.04\linewidth]{rates_outflow.png}
        \caption{Materials flows rates for the protactinium decay tank during 
        \gls{MSBR} online reprocessing.}
        \label{fig:outflow}
\end{figure}
As shown in Figure~\ref{fig:outflow}, the tank for protactinium decay 
accumulates $^{233}$Pa for approximately 200 days. Fresh $^{233}$U fuel flow is 
also established after 200 days. Uranium produced in the tank by protactinium 
decay is separated by circulation of the salt through a flourinator. The fully 
processed molten salt, on its way back to the primary loop, has uranium added 
at the rate required to maintain or adjust the fissile material concentration 
and, hence, the reactivity, in the reactor core as desired.
